### 2017-11-16 cv-body.tex
Add to cv
Not open access
Fix conflicts
Update cv

\begin{description}
\tightlist
\item[2017]
Aquatic Science Biologist and Program Head in Spatial Stock Assessment,
Offshore Section, Aquatic Resource Research and Assessment Division,
Pacific Biological Station, Fisheries and Oceans Canada, Nanaimo, BC,
Canada
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA, USA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University, Burnaby, BC, Canada
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University, Burnaby, BC, Canada
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie
University, Halifax, NS, Canada
\end{description}

@@

@@

resilience of a seagrass system exposed to multiple stressors. Global
Change Biology. In press. \url{https://doi.org/10.1111/gcb.13854}

@@

Eighth most-read CJFAS article in 2008.

@@

\begin{description}
\tightlist
\item[2017]
rrfields: Robust random fields for spatiotemporal modelling.
\url{https://github.com/seananderson/rrfields}
\item[2017]
datalimited: Stock assessment methods for data-limited fisheries.
\url{https://github.com/datalimited/datalimited}
\item[2014]
\textbf{Anderson, S.C.}, J.W. Moore, M.M McClure, N.K. Dulvy, A.B.
Cooper.\\
metafolio: Metapopulation simulations for conserving salmon through
portfolio optimization.
\url{http://cran.r-project.org/package=metafolio}
\item[2013]
\textbf{Anderson, S.C.}, C.C. Monnahan, K.F. Johnson, K. Ono, J.L.
Valero, C.J Cunningham, F. Hurtado-Ferro, R. Licandeo, C.R. McGilliard,
C.S. Szuwalski, K.A. Vert-pre, A.R. Whitten. ss3sim: Fisheries stock
assessment simulation testing with Stock Synthesis.
\url{http://cran.r-project.org/package=ss3sim}
\item[2013]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. ecofolio: Tools to
quantify metapopulation portfolio effects.
\url{https://github.com/seananderson/ecofolio}
\end{description}

@@

\begin{description}
\tightlist
\item[2017]
\textbf{Anderson, S.C.} Data-driven approaches to quantifying population
status and extremes. Early Career Award keynote lecture at the Canadian
Society for Ecology and Evolution (CSEE), Victoria, BC, Canada.
\item[2016]
\textbf{Anderson, S.C.}, T.A. Branch, A.B. Cooper, N.K. Dulvy.
Black-swan events in animal populations. North America Congress for
Conservation Biology, Madison, WI, United States.
\item[2016]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, M. Dickey-Collas, K.M. Kleisner, C. Longo, G.C.
Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig. Improving
estimates of population status and trend with superensemble models.
World Fisheries Conference, Busan, South Korea. (Presented \emph{in
absentia} by J.T. Thorson.)
\item[2015]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, M. Dickey-Collas, K.M. Kleisner, C. Longo, G.C.
Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig. Improving
estimates of population status and trend with superensemble models.
American Fisheries Society Annual Meeting, Portland, OR, United States.
\item[2013]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. False prophets: The
challenges of quantifying ecological portfolios
(\href{http://seananderson.ca/talks/2013/PE_SAFS_quantsem.pdf}{slides}),
Quantitative Seminar, School of Aquatic and Fishery Sciences, University
of Washington, Seattle, WA, United States.
\item[2012]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. False prophets: The
ecological portfolio effect overestimates the benefit of diversity.
Branch Lab, School of Aquatic and Fishery Sciences, University of
Washington, Seattle, WA, United States.
\item[2012]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. Metapopulation
dynamics and the generality of the ecological portfolio effect. Les
Ecologistes Departmental Seminar, Simon Fraser University, Burnaby, BC,
Canada.
\item[2010]
\textbf{Anderson, S.C.} The rise of invertebrates, the fall of sea
cucumbers, and the risk of maturing late. Earth2Ocean Research Group,
Simon Fraser University, Burnaby, BC, Canada.
\item[2009]
\textbf{Anderson, S.C.}, J.E. Mills Flemming, R. Watson, H.K. Lotze.
Ecosystem impacts of the global expansion of invertebrate fisheries.
International Oceans Past II Conference \emph{Multidisciplinary
Perspectives on the History and Future of Marine Animal Populations}.
Vancouver, BC, Canada.
\item[2009]
\textbf{Anderson, S.C.}, J.E Mills Flemming, R. Watson, H.K. Lotze.
Global invertebrate fisheries: trends and consequences. NCEAS (National
Center for Ecological Analysis and Synthesis) Working Group
\emph{Finding Common Ground in Marine Conservation and Management}.
Santa Barbara, CA, USA.
\item[2009]
\textbf{Anderson, S.C.}, H.K. Lotze, N.L. Shackell. Evaluating the
knowledge base for expanding low-trophic level fisheries in Atlantic
Canada. Harvest Fisheries Seminar Series. Bedford Institute of
Oceanography, Fisheries and Oceans, Dartmouth, NS, Canada.
\item[2008]
\textbf{Anderson, S.C.}, H.K. Lotze, N.L. Shackell. Evaluating the
knowledge base for expanding low-trophic level fisheries in Atlantic
Canada. Departmental Seminar, Biology Department, Dalhousie University,
Canada.
\end{description}

@@

\begin{description}
\tightlist
\item[2015-16]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) \emph{Applying portfolio effects to the Gulf of Alaska
ecosystem: Did multi-scale diversity buffer against the Exxon Valdez oil
spill?} (\href{https://www.nceas.ucsb.edu/featured/marshall}{URL})
\item[2015-16]
Gordon and Betty Moore Foundation funded working group \emph{Applying
data-limited stock status models and developing management guidance for
unassessed fish stocks}.
\item[2011--13]
NESCent (National Evolutionary Synthesis Center, Durham, NC) Working
Group \emph{Determinants of Extinction in Ancient and Modern Seas} led
by Paul Harnik, Seth Finnegan, and Rowan Lockwood.
(\href{http://www.nescent.org/science/awards_summary.php?id=256}{URL})
\item[2010]
Atlantic Halibut Assessment Science Peer Review Meeting, Fisheries and
Oceans, Dartmouth, NS, Canada.
\item[2007--09]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) Distributed Graduate Seminar, in association with the
Working Group \emph{Finding Common Ground in Marine Conservation and
Management} led by Ray Hilborn and Boris Worm.
(\href{http://www.nceas.ucsb.edu/projects/12307}{URL})
\item[2008]
Workshop on Canadian Science and Management Strategies for Sea Cucumber
(\emph{Cucumaria frondosa}), Fisheries and Oceans, Dartmouth, NS, Canada
(work presented \emph{in absentia}).
\item[2007]
Workshop on Canadian Science and Management Strategies for Atlantic
Hagfish, Fisheries and Oceans, Dartmouth, NS, Canada.
(\href{http://www.dfo-mpo.gc.ca/CSAS/Csas/Publications/Pro-CR/2009/2009_009_e.htm}{URL})
\end{description}

@@

\begin{description}
\tightlist
\item[Present]
Proficient in statistical analyses and data management using R, Stan,
JAGS, Sweave, knitr, Shiny, LaTeX, Git, TMB, SQL. Familiar with ADMB.
\item[2016]
Diversity in Conservation Biology, facilitated by Yolanda L. Comedy,
Director of the American Association for the Advancement of Science
(AAAS) Center for Advancing Science \& Engineering Capacity
\item[2015--16]
Powerful Presentation Skills and Media Training with Teresa Erickson and
Tim Ward of Intermedia Communications, authors of
\href{https://www.amazon.com/Master-Communicators-Handbook-Teresa-Erickson/dp/1785351532}{\emph{The
Master Communicator's Handbook}}
\item[2013]
Quantitative Modelling in Ecosystem Based Management. R. Hilborn, School
of Aquatic and Fishery Sciences, University of Washington (audited).
\item[2013]
Applied Time Series Analysis. E. Holmes, M. Scheuerell, and E. Ward;
School of Aquatic and Fishery Sciences, University of Washington
(audited).
\item[2012]
Numerical Computing for the Natural Resources. A.E. Punt, School of
Aquatic and Fishery Sciences, University of Washington (audited).
\item[2012]
Risk Assessment and Decision Analysis for Management of Natural
Resources. R.M. Peterman, School of Resource and Environmental
Management, Simon Fraser University.
\item[2011]
Presenting Data and Information. Edward Tufte, Seattle, WA, United
States.
\end{description}

@@

Reviewer for Science, Ecology, Ecological Applications, Conservation
Biology, Fish and Fisheries, Marine Policy, Population Ecology, Journal
of Applied Ecology, International Journal of Tropical Biology and
Conservation, Journal of Environmental Management, Endangered Species
Research, Aquatic Conservation

>>>>

\begin{description}
\tightlist
\item[2017]
Senior Aquatic Science Biologist and Program Head in Spatial Stock
Assessment, Offshore Section, Aquatic Resource Research and Assessment
Division, Pacific Biological Station, Fisheries and Oceans Canada,
Nanaimo, BC, Canada
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA, USA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University, Burnaby, BC, Canada
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University, Burnaby, BC, Canada
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie
University, Halifax, NS, Canada
\end{description}

@@

Ward, E.J., \textbf{S.C. Anderson}, A.O. Shelton, R.E. Brenner,
M.D.\ Adkison, A.H. Beaudreau,.T. Watson, J.C. Shriver, A.C. Haynie, B.C.
Williams. Effects of increased specialization and hatchery production on
revenue variability of Alaskan salmon fishers. In press at Journal of
Applied Ecology.
\textbf{Anderson, S.C.}, T.A. Branch, A.B. Cooper, N.K. Dulvy. Reply to
Youngflesh and Lynch: Migration and population growth rate in animal
black-swan events. Proceedings of the National Academy of Sciences. In
press at Proceedings of the National Academy of Sciences.
\url{https://doi.org/10.1073/pnas.1714157114}

@@

resilience of a seagrass system exposed to multiple stressors. In press
at Global Change Biology. \url{https://doi.org/10.1111/gcb.13854}

@@

@@

\begin{description}
\tightlist
\item[2017]
E.J. Ward, \textbf{Anderson, S.C.} bayesdfa: Bayesian Dynamic Factor
Analysis (DFA) with Stan. \url{https://github.com/fate-ewi/bayesdfa}
\item[2017]
\textbf{Anderson, S.C.}, E.J. Ward. glmmfields: GLMMs with robust random
fields for spatial and spatiotemporal modelling.
\url{https://github.com/seananderson/glmmfields}
\item[2016]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, J. Afflerbach, M. Dickey-Collas, K.M. Kleisner, C.
Longo, G.C. Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig.
datalimited: Stock Assessment Methods for Data-limited Fisheries.
\url{https://github.com/datalimited/datalimited}
\item[2014]
\textbf{Anderson, S.C.}, J.W. Moore, M.M McClure, N.K. Dulvy, A.B.
Cooper.\\
metafolio: Metapopulation simulations for conserving salmon through
portfolio optimization.
\url{http://cran.r-project.org/package=metafolio}
\item[2013]
\textbf{Anderson, S.C.}, C.C. Monnahan, K.F. Johnson, K. Ono, J.L.
Valero, C.J Cunningham, F. Hurtado-Ferro, R. Licandeo, C.R. McGilliard,
C.S. Szuwalski, K.A. Vert-pre, A.R. Whitten. ss3sim: Fisheries stock
assessment simulation testing with Stock Synthesis.
\url{http://cran.r-project.org/package=ss3sim},
\url{https://github.com/ss3sim/ss3sim}
\item[2013]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. ecofolio: Tools to
quantify metapopulation portfolio effects.
\url{https://github.com/seananderson/ecofolio}
\end{description}

@@

\begin{description}
\tightlist
\item[2017]
\textbf{Anderson, S.C.}, E.J. Ward, A.O. Shelton. Benefits and risks of
diversification for individual fishers in Alaska, 1975--2015. NOAA
National Ocean Service Science Seminar. Presented remotely to
Washington, DC and other NOAA participants.
\item[2017]
\textbf{Anderson, S.C.} Data-driven approaches to quantifying population
status and extremes. Early Career Award keynote lecture at the Canadian
Society for Ecology and Evolution (CSEE), Victoria, BC, Canada.
\item[2016]
\textbf{Anderson, S.C.}, T.A. Branch, A.B. Cooper, N.K. Dulvy.
Black-swan events in animal populations. North America Congress for
Conservation Biology, Madison, WI, United States.
\item[2016]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, M. Dickey-Collas, K.M. Kleisner, C. Longo, G.C.
Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig. Improving
estimates of population status and trend with superensemble models.
World Fisheries Conference, Busan, South Korea. (Presented \emph{in
absentia} by J.T. Thorson.)
\item[2015]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, M. Dickey-Collas, K.M. Kleisner, C. Longo, G.C.
Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig. Improving
estimates of population status and trend with superensemble models.
American Fisheries Society Annual Meeting, Portland, OR, United States.
\item[2013]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. False prophets: The
challenges of quantifying ecological portfolios
(\href{http://seananderson.ca/talks/2013/PE_SAFS_quantsem.pdf}{slides}),
Quantitative Seminar, School of Aquatic and Fishery Sciences, University
of Washington, Seattle, WA, United States.
\item[2012]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. False prophets: The
ecological portfolio effect overestimates the benefit of diversity.
Branch Lab, School of Aquatic and Fishery Sciences, University of
Washington, Seattle, WA, United States.
\item[2012]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. Metapopulation
dynamics and the generality of the ecological portfolio effect. Les
Ecologistes Departmental Seminar, Simon Fraser University, Burnaby, BC,
Canada.
\item[2010]
\textbf{Anderson, S.C.} The rise of invertebrates, the fall of sea
cucumbers, and the risk of maturing late. Earth2Ocean Research Group,
Simon Fraser University, Burnaby, BC, Canada.
\item[2009]
\textbf{Anderson, S.C.}, J.E. Mills Flemming, R. Watson, H.K. Lotze.
Ecosystem impacts of the global expansion of invertebrate fisheries.
International Oceans Past II Conference \emph{Multidisciplinary
Perspectives on the History and Future of Marine Animal Populations}.
Vancouver, BC, Canada.
\item[2009]
\textbf{Anderson, S.C.}, J.E Mills Flemming, R. Watson, H.K. Lotze.
Global invertebrate fisheries: trends and consequences. NCEAS (National
Center for Ecological Analysis and Synthesis) Working Group
\emph{Finding Common Ground in Marine Conservation and Management}.
Santa Barbara, CA, USA.
\item[2009]
\textbf{Anderson, S.C.}, H.K. Lotze, N.L. Shackell. Evaluating the
knowledge base for expanding low-trophic level fisheries in Atlantic
Canada. Harvest Fisheries Seminar Series. Bedford Institute of
Oceanography, Fisheries and Oceans, Dartmouth, NS, Canada.
\item[2008]
\textbf{Anderson, S.C.}, H.K. Lotze, N.L. Shackell. Evaluating the
knowledge base for expanding low-trophic level fisheries in Atlantic
Canada. Departmental Seminar, Biology Department, Dalhousie University,
Canada.
\end{description}

@@

\begin{description}
\tightlist
\item[2016--17]
NOAA Fisheries and the Environment (FATE) working group \emph{An
early-warning index for abrupt change in northeast Pacific ecosystems}.
\item[2015-16]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) \emph{Applying portfolio effects to the Gulf of Alaska
ecosystem: Did multi-scale diversity buffer against the Exxon Valdez oil
spill?} (\href{https://www.nceas.ucsb.edu/featured/marshall}{URL})
\item[2015-16]
Gordon and Betty Moore Foundation funded working group \emph{Applying
data-limited stock status models and developing management guidance for
unassessed fish stocks}.
\item[2011--13]
NESCent (National Evolutionary Synthesis Center, Durham, NC) Working
Group \emph{Determinants of Extinction in Ancient and Modern Seas} led
by Paul Harnik, Seth Finnegan, and Rowan Lockwood.
(\href{http://www.nescent.org/science/awards_summary.php?id=256}{URL})
\item[2010]
Atlantic Halibut Assessment Science Peer Review Meeting, Fisheries and
Oceans, Dartmouth, NS, Canada.
\item[2007--09]
NCEAS (National Center for Ecological Analysis and Synthesis, Santa
Barbara, CA) Distributed Graduate Seminar, in association with the
Working Group \emph{Finding Common Ground in Marine Conservation and
Management} led by Ray Hilborn and Boris Worm.
(\href{http://www.nceas.ucsb.edu/projects/12307}{URL})
\item[2008]
Workshop on Canadian Science and Management Strategies for Sea Cucumber
(\emph{Cucumaria frondosa}), Fisheries and Oceans, Dartmouth, NS, Canada
(work presented \emph{in absentia}).
\item[2007]
Workshop on Canadian Science and Management Strategies for Atlantic
Hagfish, Fisheries and Oceans, Dartmouth, NS, Canada.
(\href{http://www.dfo-mpo.gc.ca/CSAS/Csas/Publications/Pro-CR/2009/2009_009_e.htm}{URL})
\end{description}

@@

\begin{description}
\tightlist
\item[2016]
Diversity in Conservation Biology, facilitated by Yolanda L. Comedy,
Director of the American Association for the Advancement of Science
(AAAS) Center for Advancing Science \& Engineering Capacity
\item[2015--16]
Powerful Presentation Skills and Media Training with Teresa Erickson and
Tim Ward of Intermedia Communications, authors of
\href{https://www.amazon.com/Master-Communicators-Handbook-Teresa-Erickson/dp/1785351532}{\emph{The
Master Communicator's Handbook}}
\item[2013]
Applied Time Series Analysis. E. Holmes, M. Scheuerell, and E. Ward;
School of Aquatic and Fishery Sciences, University of Washington
(audited).
\item[2012]
Numerical Computing for the Natural Resources. A.E. Punt, School of
Aquatic and Fishery Sciences, University of Washington (audited).
\item[2012]
Risk Assessment and Decision Analysis for Management of Natural
Resources. R.M. Peterman, School of Resource and Environmental
Management, Simon Fraser University.
\item[2011]
Presenting Data and Information. Edward Tufte, Seattle, WA, United
States.
\end{description}

@@

Reviewer for Science, Ecology, Ecological Applications, Conservation
Biology, Fish and Fisheries, Marine Policy, Population Ecology, Journal
of Applied Ecology, ICES Journal of Marine Science, International
Journal of Tropical Biology and Conservation, Journal of Environmental
Management, Endangered Species Research, Aquatic Conservation
